Robots, Are They Overlords or Serf-Laborers?

### 2015-06-09 draft1.tex
Format all citation w/ bibtex

Even though the term robot was coined two centuries ago and the idea of Artificial Intelligence (AI) emerged decades ago, some of the problems that have been raised by these two terms are yet to solved. Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details. Thus, this paper focuses on numerous definitions for these terms and various applications of AI.\par

@@

Along with the definitions of Robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots. \citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot. Although \citeA{pear} excludes any means of social interaction in the definitions of Robotics proposed in this article, \citeA(rod) exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells. Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within Robotics exemplifies another complex issue. The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace that of the wisdom regarding robots and ourselves.\par

@@

One common definition of AI is cited by Bostrom (n.d.), “A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills.” This definition clearly distinguishes specific domain intelligent agents and AI. Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that Duffy (2006, p. 34) speculates. 

@@

sophisticated hardware was developed. For instance, the invention of faster Central Processor Units ledresearchers to have more calculation power and create more detailed and elaborate algorithms (Bostrom, n.d.). Alan Turing, who is regarded the one who sets the basis for AI, created a test to question a machine's ability in its intelligence (Grebelsky, Lisin, \& Oks, n.d.). The second milestone of AI is invention of a programming language, Lisp (list processing), in the laboratories of Massachusetts Institute of Technology. Even though the concepts of AI existed before Lisp, it enabled researchers to use symbolic objects rather than numbers which was a major obstacle of AI creation. The other issue precluding the creation of AI is the challenges of information collection. As mentioned above, emulation of human cognitive and perceptual process have been a major method to implement AI. For that reason, natural language comprehension and visual information recognition have become two main focuses in AI research. Another example of the imitation of humanistic features is the structure of the human brain. The emergence of brand new sophisticated algorithms, namely, artificial neural networks and deep learning, also show significant resemblance to neural structure of the human brain which has

@@

Bryson (2015) claims that the common societal problems, such as the inequitable income distribution and poverty resulting from overpopulation, are impossible to cope with using regular tools and paradigms which governments now have. Having been scrutinizing social sciences, namely, developmental psychology and sociology, researchers might expand their interpretation of human behaviors which might enable them find new solutions for the given problems. Moreover, elimination of aging and eradication of diseases might be the possible consequence of the creation of AI (Bostrom, n.d.). Both authors discuss AI's advanced reasoning and interpretation underlining the new opportunities that AI might bring to societies in order to solve chronic societal problems.

@@

By its definition, AI appears to provide the fastest and the optimal solutions for the problems that is given which depends on supreme decision-making and cognitive processes that of humans. Consequently, this advanced techniques will likely to provide a privilege to have our problems solved with the help of AI. In other words, thanks to outstripping abilities of AI, humans might not need to invent any other tool to solve problems (Bostrom, n.d.).

@@

Bostrom (n.d.) also discusses that AI might deliberately elaborate its structure and source code to enhance its abilities resulting in more advanced superintelligence, which will result in more complex structure of AI and calculation power.

@@

From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems. Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society (Duffy, 2006). This section synthesizes the ethical issues and counterarguments coping with them.

@@

Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, a major issue having been discussed is whether or not military, one of the biggest supporter of AI, is being sincere with its funding (Grebelsky et al., n.d.). Of the many supporters of AI, military appears to be the most questionable one due to plausible intentions of creation of humanoid army. The ultimate reason of AI which is elevation of life conditions and inquiry for the chronic problems of our societies notwithstanding, utilization of weaponized robotic army would increment the vast possession of ammunition and weaponization problem rather than solving our problems.\par
Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, Grebelsky et al. (n.d.) claims that combination of these factors would make AI able to easily reproduce itself, which means robots may own robots that they create in the long term. Consequently, second generations robots created by the first generations would be utterly

@@

The rise of computers which has led the employment of robots in industry lessen the human employment starting from late 70's. Because of the downsizing tendency of corporation which resulted from this replacement, millions of low-skilled workers lost their jobs. Given that fact, Grebelsky et al. (n.d.) predicts the aftermath of the creation of AI. This vast computation power might replace most of the low-skilled laborers with the more powerful robots. In the light of that prediction, highly developed economies may show an extensive recession.\par

@@

In addition to former arguments, Rosas (2012) proposes yet another. Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession

@@

Since self-awareness of AI, it can be regarded as an independent agent. This conceptual independency, however, raises a ethical dilemma. Many researchers has been questioning whether or not superintelligent agents have duties to the society and to what extent governments give social rights Roberts (2004). Given that approach, Krebs (2006) mentions early speculations of social equality
regarding civil and political rights among robots and humans in Japanese anime and mangas which artworks are consisted of futuristic plots including robots cohabitating and interacting with humans. These questions caused by the legal ramification of AI. Grebelsky (n.d.) discusses that it is not obvious that who will be responsible for results of AI's actions. Not only does AI's position in the society matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa. \par
The counterargument was proposed by Rosas (2012) by underlining the evolutionary approach on human morality. As Rosas (2012) cited, probability of error in evolution of human morality and nature displays a significant resemblance to the errors that might AI commit. For that reason, it is more logical to create a ground that can tolerate the probable AI's errors.

@@

One issue that discussed among scholars is whether or not creating a self-aware machine which is able to reason in the same level with human intelligence would be stealing the role of God. In addition to that issue, almost all of the monotheistic religions put significant emphasis on the features of God concept. According to these religions, God himself is unique and incomparably exceptional than the ones what he created. Of the many major sins, imitating God, or in other words one's God-like manifestation, is the unforgivable one. Grebelsky et al. (n.d.) discusses this issue by showing the similarities of creation of a self-aware agent and creation concept of God. Moreover, Duffy (2006) mentions human-like form that researchers tend to build social robots, an example of embodiment of AI. In the light of these facts, the concept of God and the creation of AI seems to intersect to some extent.\par
The counterarguments put significance on more God and abilities that humans given by him rather than the limitations provided by the rules of religions. This approach to research and development of AI considers human and nature the masterpiece of God. For instance, brain is one the biggest resource that provided by God in order to make humans able to create tools and techniques to solve their problems, namely, taming the nature, building societies and elevating one's position in these societies. From this perspective, AI would be the best use of brain to commit what God orders (Grebelsky et al., n.d.).

>>>>

\citeA{bost} \citeA{bry} \citeA{bob} \citeA{gre} \citeA{rosa} \citeA{duff}
Even though the term robot was coined two centuries ago and the idea of (AI) emerged decades ago, some of the problems that have been raised by these two terms are yet to solved. Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details. Thus, this paper focuses on numerous definitions for these terms and various applications of AI.\par

@@

Along with the definitions of Robotics, the applications of it extensively vary which makes it hard to define or understand the task and the responsibilities of robots. \citeA{lan} gives different examples from a software tailored for "Jeopardy" to a teacher robot. Although \citeA{pear} excludes any means of social interaction in the definitions of Robotics proposed in this article, \citeA{rodhan} exemplifies an emerging application of robotics, a molecular level robot which identifies cancerous cells and attach them by releasing antibodies, thereby eliminating cancerous cells. Even though, experts have not been able to solve dilemma within the field of robotics, this case of sophistication within Robotics exemplifies another complex issue. The reason why these social interaction dilemma matter, whether in bodily level or molecular level, is that technology advances in faster pace that of the wisdom regarding robots and ourselves.\par

@@

One common definition of AI is cited by \citeA{bost}, "A super-intelligence is any intellect that is vastly outperforms the best human brains in practically every field, including scientific creativity, general wisdom and social skills." This definition clearly distinguishes specific domain intelligent agents and AI. Based on this definition a computer system, Deep Blue, which is a well-known computer system for its success in chess can be considered smart within a narrow domain rather than a genuine AI supported by limitations that \citeauthor{duff} \citeyear[p.~34]{duff} speculates. 

@@

sophisticated hardware was developed. For instance, the invention of faster Central Processor Units led researchers to have more calculation power and create more detailed and elaborate algorithms \cite{bost} Alan Turing, who is regarded the one who sets the basis for AI, created a test to question a machine's ability in its intelligence \cite{gre}. The second milestone of AI is invention of a programming language, Lisp (list processing), in the laboratories of Massachusetts Institute of Technology. Even though the concepts of AI existed before Lisp, it enabled researchers to use symbolic objects rather than numbers which was a major obstacle of AI creation. The other issue precluding the creation of AI is the challenges of information collection. As mentioned above, emulation of human cognitive and perceptual process have been a major method to implement AI. For that reason, natural language comprehension and visual information recognition have become two main focuses in AI research. Another example of the imitation of humanistic features is the structure of the human brain. The emergence of brand new sophisticated algorithms, namely, artificial neural networks and deep learning, also show significant resemblance to neural structure of the human brain which has

@@

\citeA{bry} claims that the common societal problems, such as the inequitable income distribution and poverty resulting from overpopulation, are impossible to cope with using regular tools and paradigms which governments now have. Having been scrutinizing social sciences, namely, developmental psychology and sociology, researchers might expand their interpretation of human behaviors which might enable them find new solutions for the given problems. Moreover, elimination of aging and eradication of diseases might be the possible consequence of the creation of AI /citeA{bost}. Both authors discuss AI's advanced reasoning and interpretation underlining the new opportunities that AI might bring to societies in order to solve chronic societal problems.

@@

By its definition, AI appears to provide the fastest and the optimal solutions for the problems that is given which depends on supreme decision-making and cognitive processes that of humans. Consequently, this advanced techniques will likely to provide a privilege to have our problems solved with the help of AI. In other words, thanks to outstripping abilities of AI, humans might not need to invent any other tool to solve problems \cite{bost}.

@@

\citeA{bost} also discusses that AI might deliberately elaborate its structure and source code to enhance its abilities resulting in more advanced superintelligence, which will result in more complex structure of AI and calculation power.

@@

From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems. Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society \cite{duff}. This section synthesizes the ethical issues and counterarguments coping with them.

@@

Since robots can be regarded self-conscience agents, thanks to advanced reasoning, cognitive and perceptual abilities provided by AI, a major issue having been discussed is whether or not military, one of the biggest supporter of AI, is being sincere with its funding \cite{gre}. Of the many supporters of AI, military appears to be the most questionable one due to plausible intentions of creation of humanoid army. The ultimate reason of AI which is elevation of life conditions and inquiry for the chronic problems of our societies notwithstanding, utilization of weaponized robotic army would increment the vast possession of ammunition and weaponization problem rather than solving our problems.\par
Although being able to elaborate its source code by itself and being easily cloned are the factors considered advantage for the society, \citeA{duff} claims that combination of these factors would make AI able to easily reproduce itself, which means robots may own robots that they create in the long term. Consequently, second generations robots created by the first generations would be utterly

@@

The rise of computers which has led the employment of robots in industry lessen the human employment starting from late 70's. Because of the downsizing tendency of corporation which resulted from this replacement, millions of low-skilled workers lost their jobs. Given that fact, \citeA{gre} predicts the aftermath of the creation of AI. This vast computation power might replace most of the low-skilled laborers with the more powerful robots. In the light of that prediction, highly developed economies may show an extensive recession.\par

@@

In addition to former arguments, \citeA{rosa} proposes yet another. Even though researchers, for instance, want to create a narrow-domain savvy robot, the robot may want to change its profession

@@

Since self-awareness of AI, it can be regarded as an independent agent. This conceptual independency, however, raises a ethical dilemma. Many researchers has been questioning whether or not superintelligent agents have duties to the society and to what extent governments give social rights \cite{bob}. Given that approach, \cite{kerb} mentions early speculations of social equality regarding civil and political rights among robots and humans in Japanese anime and mangas which artworks are consisted of futuristic plots including robots cohabitating and interacting with humans. These questions caused by the legal ramification of AI. \citeA{gre} discusses that it is not obvious that who will be responsible for results of AI's actions. Not only does AI's position in the society matter, but it is also equally important for governments to decide the AI's responsibility for the society, vice versa. \par
The counterargument was proposed by \citeA{rosa} by underlining the evolutionary approach on human morality. As \citeA{rosa} cited, probability of error in evolution of human morality and nature displays a significant resemblance to the errors that might AI commit. For that reason, it is more logical to create a ground that can tolerate the probable AI's errors.

@@

One issue that discussed among scholars is whether or not creating a self-aware machine which is able to reason in the same level with human intelligence would be stealing the role of God. In addition to that issue, almost all of the monotheistic religions put significant emphasis on the features of God concept. According to these religions, God himself is unique and incomparably exceptional than the ones what he created. Of the many major sins, imitating God, or in other words one's God-like manifestation, is the unforgivable one.\citeA{gre} discusses this issue by showing the similarities of creation of a self-aware agent and creation concept of God. Moreover, \citeA{duff} mentions human-like form that researchers tend to build social robots, an example of embodiment of AI. In the light of these facts, the concept of God and the creation of AI seems to intersect to some extent.\par
The counterarguments put significance on more God and abilities that humans given by him rather than the limitations provided by the rules of religions. This approach to research and development of AI considers human and nature the masterpiece of God. For instance, brain is one the biggest resource that provided by God in order to make humans able to create tools and techniques to solve their problems, namely, taming the nature, building societies and elevating one's position in these societies. From this perspective, AI would be the best use of brain to commit what God orders \cite{gre}.
